Energy and the CES production function

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Beginnings of a sigma graph.

@@

Table~\ref{tab:CES_sr_gof} shows estimated values of
the scale parameter~($\theta$),
the Solow residual~($\lambda$), and
goodness of fit~($sse$)
for all modeling choices.

<<Table_data>>=
table_data <- AllCoeffs 
table_data <- plyr::rename(table_data, c("model" = "Model", 
                                         "energy" = "Energy", 
                                         "nest" = "Nest"))
table_data$Nest <- plyr::mapvalues(table_data$Nest,
                                   from=c("kl", "kle", "lek", "ekl"),
                                   to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$"))
table_data$CSP <- plyr::mapvalues(table_data$CSP, 
                                  from=c("Adhere to CSP", "Reject CSP"), 
                                  to=c("Adhere", "Reject"))
table_data$Energy <- plyr::mapvalues(table_data$Energy, 
                                     from=c("Without energy", "With energy"), 
                                     to=c("Without", "With"))
table_data$model <- plyr::mapvalues(table_data$model, 
                                    from=c("exp"), 
                                    to=c("Ref."))
@

<<CES_sr_gof, results="asis">>=
data_CES_SR_gof <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, flavor, Energy, Nest, CSP, scale, lambda, sse)
data_CES_SR_gof <- plyr::rename(data_CES_SR_gof, c("flavor" = "Factors of prod.",
                                                   "scale" = "$\\theta$",
                                                   "lambda" = "$\\lambda$"))
myXTable(data_CES_SR_gof,
         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_alpha, results="asis">>=
data_CES_alpha <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, flavor, Energy, Nest, CSP, alpha_1, alpha_2, alpha_3)
data_CES_alpha <- plyr::rename(data_CES_alpha, c("flavor" = "Factors of prod.",
                                                 "alpha_1" = "$\\alpha_k$",
                                                 "alpha_2" = "$\\alpha_l$",
                                                 "alpha_3" = "$\\alpha_e$"))
myXTable(data_CES_alpha,
         caption="Output elasticities~($\\alpha$) for all models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
                                                     "sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
                                                     "sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

>>>>

%++++++++++++++++++++++++++++++
\subsection{$\sigma$ graph} 
\label{sec:sigma_graph}
%++++++++++++++++++++++++++++++

<<sigma_graph>>=
sigma_graph_data <- filter(AllCoeffs, model=="CES") %>% 
  select(Country, CSP, flavor, energy, nest, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2)
# Change nest to a nicer-looking nest string
sigma_graph_data$nest <- plyr::mapvalues(sigma_graph_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("kl", "(kl)e", "(le)k", "(ek)l"))
# Now melt the data
sigma_graph_data <- melt(sigma_graph_data, 
                         measure.vars = c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"), 
                         value.name = "value", 
                         variable.name = "variable")
# Create labels
sigma_graph_data$label <- paste(sigma_graph_data$CSP, sigma_graph_data$flavor, 
                                sigma_graph_data$energy, sigma_graph_data$nest, 
                                sigma_graph_data$variable, sep=", ")
sigma_graph_data <- na.omit(sigma_graph_data)

# Make the plot
plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  # scale_x_discrete(limits=rev(order)) +
  ylab("") +
#   scale_y_continuous(breaks=c(0, 0.5, 1)) + 
  guides(fill=guide_legend(title=NULL)) +
  scale_fill_brewer(palette="OrRd") +
  coord_flip() + 
  xy_theme() +
  theme(axis.ticks.y = element_blank())
plot # for debugging
@

@@

Table~\ref{tab:CES_sr_gof} shows estimated values of
the scale parameter~($\theta$),
the Solow residual~($\lambda$), and
goodness of fit~(SSE)
for all modeling choices.

<<Table_data>>=
table_data <- AllCoeffs 
table_data <- plyr::rename(table_data, c("model" = "Model", 
                                         "energy" = "Energy", 
                                         "nest" = "Nest"))
table_data$Nest <- plyr::mapvalues(table_data$Nest,
                                   from=c("kl", "kle", "lek", "ekl"),
                                   to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$"))
table_data$CSP <- plyr::mapvalues(table_data$CSP, 
                                  from=c("Adhere to CSP", "Reject CSP"), 
                                  to=c("Adhere", "Reject"))
table_data$Energy <- plyr::mapvalues(table_data$Energy, 
                                     from=c("Without energy", "With energy"), 
                                     to=c("Without", "With"))
table_data$Model <- plyr::mapvalues(table_data$Model, 
                                    from=c("exp"), 
                                    to=c("Ref."))
@

<<CES_sr_gof, results="asis">>=
data_CES_SR_gof <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse)
data_CES_SR_gof <- plyr::rename(data_CES_SR_gof, c("flavor" = "Factors of prod.",
                                                   "scale" = "$\\theta$",
                                                   "lambda" = "$\\lambda$"))
myXTable(data_CES_SR_gof,
         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_alpha, results="asis">>=
data_CES_alpha <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3)
data_CES_alpha <- plyr::rename(data_CES_alpha, c("flavor" = "Factors of prod.",
                                                 "alpha_1" = "$\\alpha_k$",
                                                 "alpha_2" = "$\\alpha_l$",
                                                 "alpha_3" = "$\\alpha_e$"))
myXTable(data_CES_alpha,
         caption="Output elasticities~($\\alpha$) for all models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- filter(table_data, Model=="CES") %>% 
  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
                                                     "sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- filter(table_data, Model=="CES") %>% 
  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
                                                     "sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
